An item response theory analysis of the matrix reasoning item bank (MaRs-IB)

### 2022-01-21 manuscript/main.tex
updates to manuscript

\begin{equation}
p(y_{ijk} = 1) = \gamma_{jk} + (1-\gamma_{jk}) \cdot \text{logit}^{-1} \left( \alpha_{jk} \cdot \theta_i - \beta_{jk} \right)
\end{equation}

@@

\begin{equation}
\theta_i = \sum_{p=1}^P X_{ip} \rho_p + \epsilon_i    
\end{equation}

@@

\section{Test assembly}

@@

\subsection{Convergent validity}

To measure convergent validity, blah blah blah. Need to write model here. Or should we write above?

@@

>>>>

\begin{equation} \label{eq:1}
p(y_{ijk} = 1) = \gamma_{jk} + (1-\gamma_{jk}) \cdot \text{logit}^{-1} \left( \alpha_{jk} \cdot \theta_i - \beta_{jk} \right)
\end{equation}

@@

\begin{equation} \label{eq:4}
\theta_i = \sum_{p=1}^P X_{ip} \rho_p + \epsilon_i    
\end{equation}

@@

\subsection{Test assembly}

@@

To measure the convergent validity between the MaRs-IB and RPM measures, we again utilized an explanatory item response model framework. Specifically we modeled participants' ability on the MaRs-IB short forms as in Eq \ref{eq:4}, this time entering participants gender, age, and total score on the RPM as covariates. Participants' individual responses were again modeled using the 3PL model (eq \ref{eq:1}), where the difficulty and discrimination parameters for each item were fixed to the posterior average as estimated in the item cloning models.

The partial correlation between total scores on the RPM and ability on the MaRs-IB was $\rho = 0.527$ (95\% HDI = 0.457 - 0.577). Given the reliability of both measures, we should not expect correlations much larger than $\rho = 0.624$ (or $0.79^2$). As such, this result indicates good convergent validity between the two matrix reasoning measures. Finally, in this smaller sample, neither age nor gender was credibly associated with performance on the MaRs-IB short forms (age: $\rho$ = -0.123, 95\% HDI = -0.253 - 0.013; gender: $\rho$ = -0.025, 95\% HDI = -0.160 - 0.108).

Would a paragraph on MaRs-IB administration time be helpful? To briefly say that participants spent, on average, 3 minutes on the MaRs-IB items making it a short and valid measure.

@@

Do we need a short discussion here or is it sufficient to simply move to general discussion?
